Internal physiology and external cues drive changes in reproductive axis of parenting pigeons

### 2020-03-06 docs/manuscript/elife_v1.Rmd
done with pub for now

>>>>

Results in context to literature.

Significance.

Limitations.

Data accessibility and reproducibility are key challenges for today's researchers. Using Binder and Shiny, we have provides a means for scientists, physicians, and the general public to explore the data, code, and results from this project at <https://raynamharris.shinyapps.io/musicalgenes/>. Like Hipposeq (Cembrowski et al elife 2016, 2018), this tools allows quick and easy data exploration of RNAseq data from mutiple cell types that relate to brain function.

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth]{../../figures/supplfig3}
  \caption{R shiny, image 1}
  \label{figure:supplfig3}
\end{figure}
